---
title: "Visualization 2"
author: "Congyu Yang"
date: "2024-10-01"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(patchwork)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = case_match(
      id, 
      "USW00094728" ~ "CentralPark_NY", 
      "USW00022534" ~ "Molokai_HI",
      "USS0023B17S" ~ "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```
Made a scatterplot but fancy this time.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin,y = tmax, color = name))+
  geom_point(alpha = 0.3) +
  labs(
    title = "Temperature scatterplot",
    x = "Minimum Temp(C)",
    y = "Maximum Temp(C)",
    color = "Location",
    caption = "Weather data taken from rnoaa package for three stations"
  ) +
  scale_x_continuous(breaks = c(-15,0,20),
                     labels = c("-15C","0","20"))+
  scale_y_continuous(
    limits = c(0,30),
    transform = "sqrt"
  )
```

Look at color

```{r}
weather_df %>% 
  ggplot(aes(x = tmin,y = tmax, color = name))+
  geom_point(alpha = 0.3) +
  labs(
    title = "Temperature scatterplot",
    x = "Minimum Temp(C)",
    y = "Maximum Temp(C)",
    color = "Location",
    caption = "Weather data taken from rnoaa package for three stations"
  ) +
  scale_color_hue(h = c(100,400)) +
  viridis::scale_color_viridis(discrete = T)
```
## Themes

```{r}
gg_scatterplot <- weather_df %>% 
  ggplot(aes(x = tmin,y = tmax, color = name))+
  geom_point(alpha = 0.3) +
  labs(
    title = "Temperature scatterplot",
    x = "Minimum Temp(C)",
    y = "Maximum Temp(C)",
    color = "Location",
    caption = "Weather data taken from rnoaa package for three stations"
  ) +
  viridis::scale_color_viridis(discrete = T)
```

```{r}
gg_scatterplot +
  theme(legend.position = "bottom")
```

Change background color
change it ahead of time, it is like resetting everything, if you do legend position first and then reset theme_bw, legend position will no longer works.

```{r}
gg_scatterplot +
  theme_bw()+
  theme(legend.position = "bottom")
```
order matters...

```{r}
gg_scatterplot +
  theme(legend.position = "bottom")+
  theme_minimal()
```

```{r}
gg_scatterplot +
  theme(legend.position = "bottom")+
  theme_classic()
```
```{r}
gg_scatterplot +
  theme(legend.position = "bottom")+
  ggthemes::theme_excel()
```
New Scatterplot

```{r}
weather_df %>% 
  ggplot(aes(x = date,y = tmax,color = name,size = prcp)) +
  geom_point(alpha = 0.3)+
  geom_smooth(se = F)+
  viridis::scale_color_viridis(discrete = T)+
  labs(
    x = "Date",
    y = "Maximum Temp (C)",
    title = "Seasonal variation ..."
  )
# not yet finished
```
Extra Bonus stuff in `ggplot`
Use different datasets in different `geom`s
```{r}
central_park_df =
  weather_df %>% 
  filter(name == "CentralPark_NY")

molokai_df =
  weather_df %>% 
  filter(name == "Molokai_HI")

molokai_df %>% 
  ggplot(aes(x = date, y = tmax,color = name))+
  geom_point()+
  geom_line(data = central_park_df)
```
## Multiple Panels

```{r}
weather_df %>% 
  ggplot(aes(x = tmax, fill = name))+
  geom_density()+
  facet_grid(. ~ name)
```

```{r}
ggp_tmax_tmin =
  weather_df %>% 
  ggplot(aes(x = tmin,y = tmax,color = name))+
  geom_point(alpha = 0.3)

ggp_tmax_density =
  weather_df %>% 
  ggplot(aes(x = tmax, fill = name))+
  geom_density()

ggp_tmax_date =
  weather_df %>% 
  ggplot(aes(x = date,y = tmax, color = name))+
  geom_point()+
  geom_smooth(se = F)

(ggp_tmax_tmin + ggp_tmax_density)/ggp_tmax_date
```
## Data Manipulation





