---
title: "Visualization with ggplot"
author: "Congyu Yang"
date: "2024-09-26"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
```

## Import the data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = case_match(
      id, 
      "USW00094728" ~ "CentralPark_NY", 
      "USW00022534" ~ "Molokai_HI",
      "USS0023B17S" ~ "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

### Making our first plot

```{r}
ggplot(weather_df,aes(x = tmin, y = tmax)) +
  geom_point() # scatterplot

ggp_weather_scatterplot =
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point() # same plot but save it inside the name
```


```{r}
weather_df %>% 
  filter(is.na(tmax))
```


```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax,color = name)) +
  geom_point(alpha = 0.3, size = 0.8)+
  geom_smooth(se = FALSE)
# alpha changes the transparency of the points and size changes the size of the points
# geom_smooth draws the line that fits the points best
```
For here, we can see there is a line for each of the name category, this is because we have `color = name` in the first line of ggplot


## Where you define aesthetics can matter

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name),alpha = 0.3, size = 0.8)+
  geom_smooth(se = FALSE)
```
Now these is only 1 regression line for the whole x and y, this is because we have aes color setting in the second line, for all x and y(stated in the first line).

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax,color = name)) +
  geom_point(alpha = 0.3, size = 0.8)+
  geom_smooth(se = FALSE)+
  facet_grid(name ~ .)

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax,color = name)) +
  geom_point(alpha = 0.3, size = 0.8)+
  geom_smooth(se = FALSE)+
  facet_grid(. ~ name)
```
`facet_grid(row_control ~ column_control)`:one picture for each of the category in the variable you stated. Put it in row or col control position on your preference.

## Let's make a somewhat more interesting scatterplot

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax,color = name,size = prcp)) +
  geom_point(alpha = 0.3)+
  geom_smooth(se = FALSE)+
  facet_grid(. ~ name)
```
### Learning Assessment

```{r}
weather_df %>% filter(name == "CentralPark_NY") %>% 
  mutate(
    tmax_fahr = tmax*(9/5) + 32,
    tmin_fahr = tmin*(9/5) + 32
    ) %>% 
  ggplot(aes(x = tmin_fahr,y = tmax_fahr))+
  geom_point()+
  geom_smooth(method = "lm",se = FALSE)
```

## Small things

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name),alpha = 0.3,size = 0.8)+
  geom_smooth(se = FALSE)
```
```{r}

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
# as the number of data inside your dataset goes large, the ggplot no longer works well, instead, we can use geom_hex
```
```{r}
weather_df %>% 
  ggplot(aes(x = tmin,y = tmax)) +
  geom_point()
```
if you want to change the color of the points, do it inside `geom_point()` rather than in `ggplot()`



